\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-06-02 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
CHANGES IN VERSION 1.5.9 -------------------------  o topN now properly updates processingData <2012-06-01 Fri>  o combineFeatures updates featureNames based on the    groupBy argument - updated demo vignette and man    accordinlgy <2012-06-01 Fri>  o additional parameters were not passed when normalise    using vsn <2012-06-01 Fri>
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@66357 bc3139a8-67e5-0310-9ffc-ced21a209358

<<make2exps2, echo=TRUE, cache=FALSE>>=
set.seed(1)
i <- sample(length(itraqdata), 35)
j <- sample(length(itraqdata), 35)
exp1 <- quantify(itraqdata[i], reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
exp2 <- quantify(itraqdata[j], reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
table(featureNames(exp1) %in% featureNames(exp2))
exp1 <- combineFeatures(exp1,
                        groupBy = fData(exp1)$ProteinAccession)
exp2 <- combineFeatures(exp2,
                        groupBy = fData(exp2)$ProteinAccession)
head(featureNames(exp1))
featureNames(exp1) <- fData(exp1)$ProteinAccession
featureNames(exp2) <- fData(exp2)$ProteinAccession
head(featureNames(exp1))
@

Setting the feature names is critical when multiple experiments are to be combined, as 
this is done using common features as defined by their names (see below).

>>>>

<<make2exps2, echo=TRUE, cache=FALSE>>=
set.seed(1)
i <- sample(length(itraqdata), 35)
j <- sample(length(itraqdata), 35)
exp1 <- quantify(itraqdata[i], reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
exp2 <- quantify(itraqdata[j], reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
table(featureNames(exp1) %in% featureNames(exp2))
exp1 <- combineFeatures(exp1,
                        groupBy = fData(exp1)$ProteinAccession)
exp2 <- combineFeatures(exp2,
                        groupBy = fData(exp2)$ProteinAccession)
head(featureNames(exp1))
head(featureNames(exp1))
@

The feature names are updated automatically by \Rfunction{combineFeatures}, using the \Robject{groupBy} argument. 
Proper feature names, reflecting the nature of the features (spectra, peptides or proteins) is critical when multiple experiments are to be combined, as this is done using common features as defined by their names (see below).
